\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Mark,
    % middleinitial=,
    lastname=Drozdov,
    email=markdrozdov0@gmail.com,
    phone= +43-650-340-61-93,
    linkedin=mark-drozdov,
    % github=,
    % website=,
    city=Vienna,
    state=Austria,
    qrcode=photo.jpeg,
    fixobjectivespacing=false
    
]

% ----- Education -----
\section{Education}

\experience{Bachelor of Science}{Software and Information Engineering}{2021}{present}{
    \noindent Vienna University of Technology
}

\experience{Bachelor of Business Administration}{Hotel Management and Operations}{2018}{2022}{
    \noindent MODUL University Vienna \newline
    Diploma thesis "The Impact of Perceived Sustainability on Blockchain Adoption in the Hospitality Industry"
}

% ----- Work Experience -----
\section{Work Experience}

\experience{susteam}{Co-Founder and CEO}{Sep 2022}{present}
{
    \achievement{
    Led product and business development for 'susteam,' a project digitizing and optimizing sustainability and ESG reports for the hospitality industry. Managed development, sales, and budgeting, and participated in the AWS First Incubator.
    }
}

\experience{Smart Ident}{Junior Operations Manager}{Mar 2022}{Oct 2024}{
    \achievement{
        Engaged with banking and insurance clients to integrate KYC/KYB solutions, translating industry needs into product specifications and monitoring application performance to ensure efficiency.
    }
}

\experience{Entrepreneurship Avenue}{Pitch Trainer}{Apr 2024}{May 2024}{
    \achievement{
    I was invited as a Pitch Trainer to help participating startups prepare for their final presentation and share my experience on the topic. Under my guidance onne of my mentees was able to secure the second place.
    }
}

\experience{Reisigo}{CTO}{Jul 2022}{Oct 2022}{
    \achievement{
    Joined the AWS First Incubator program as part of the Reisigo project, where I assisted the co-founders with my expertise in hospitality and IT. Worked closely with the founders, gathering their needs to design the customer flow and shape the digital product's user experience.
    }
}

\experience{MODUL University Vienna}{Academic Tutor}{Mar 2020}{Jun 2022}{
    \achievement{
    Hired as a tutor for Accounting and Management Control I and II, Math, and Statistics I & II at MODUL University Vienna, due to academic performance. Successfully tutored approximately 50 international students. 
    }
}

\experience{LLP “Liga Holding”}{Real Estate Development Intern}{May 2021}{Oct 2021}{
    \achievement{
    Supported business transactions with international partners in Turkey, using language skills to coordinate meetings, handle communications, and manage project timelines.
    }
}


% ----- Certifications -----

\section{Certifications}
\experience{Technical University of Vienna}{Diversity Manager}{ongoing}{}{
    \achievement{
    Entails 16 ETCS worth of classes on diversity management, technology and ethics. 
    }
}

\experience{KlimaBündnis}{Nachhaltigkeitsbericht und EU-Taxonomie-Verordnung}{Jun 2024}{}
{
    \achievement{
    Completed workshop series on ESG reporting for companies.
    }

}

% \experience{Sustainable Impact Academy}{Impact Entrepreneur}{Dec 2023}{}
% {
%     \achievement{
%     Finished a 3-months course on sustainbale entrepreneurship. 
%     }
% }

\experience{Kanzian Engineering and Consulting GmbH}{Abfallbeauftragter GEM. § 11 AWG 2002}{Sep 2023}{}
{
    \achievement{
    Copleted a university course "Zertifizierung im Umweltmanagement" with a focus on ISO14001 and EMAS II. Upon completion, I took a certification exam on Waste Management in Austria. 
    }
    
}

\experience{Frankfurt School Blockchain Center}{NFT Talents}{Oct 2022}{}
{
    \achievement{
    A deep dive into NFTs, their current and potential use-cases, the technology behind and advantages and limitations. 
    }
}

% ----- Skills -----
\section{Skills}
\noindent\begin{tabularx}{\textwidth}{@{}X@{}X@{}X@{}X@{}}
\textbf{Technical Skills}
\begin{itemize}
    % \item JavaScript (beginner)
    % \item Java (beginner)
    % \item SQL (beginner)
    % \item RStudio
    % \item Solidity (beginner)
    % \item FastAPI (beginner)
    \item Web Development (HTML, CSS)
    \item Java, JavaScript (beginner)
    \item SQL, FastAPI (beginner)
    \item RStudio
    \item Solidity (beginner)
    \item AWS Cloud (beginner)
\end{itemize}
&
\textbf{Skills}
\begin{itemize}
    \item Microsoft Office
    \item Atlassian (Jira, Confluence, Trello)
    \item Figma
    \item CRM (Zoho)
    \item Document 360
    \item Firebase, App Store Connect
\end{itemize}
&
\textbf{Languages}
\begin{itemize}
    \item English (C1)
    \item German (C1)
    \item Russian (C2)
    \item French (B1)
\end{itemize}
\end{tabularx}


% ----- Projects and Awards -----
\section{Projects and Awards}

\experience{2nd Place Winner}
{AIM Hackathon: Sustainbility meets LLM}{Oct 2024}{}
{
    \achievement{
    Led the development of a scalable tool to detect greenwashing in ESG reports using RAG and LLMs. Successfully built an automated system to highlight misleading sustainability claims and assign trustworthiness scores. 
    }
    \tech{
    Python
    }
}

\experience{Sustainable Impact Academy}{Impact Entrepreneur}{Dec 2023}{}
{
    \achievement{
    Engaged in hands-on workshops, mentoring, and business plan development. I gained a certificate upon completion and expertise in social business modeling, financing, legal aspects, and impact measurement.
    }
    \tech{
    Presenting, Teamwork
    }
}

\experience{2nd Place Winner}
{Tourism Technology Hackathon}{Nov 2023}{}
{
    \achievement{
    Our team implemented a data pipeline mapping the data from different sources and building a knowledge graph for the different tourism subjects. The result was visualized as an interactive map with the chat bot, that could help toruism destinations with data analysis and conclusions.
    }
    \tech{
    FastAPI, React
    }
}

\experience{Lip Reading app at Hackathon}
{Coding Austria}{Jul 2023}{}
{
    \achievement{
    Utilized Audio-Visual Hidden Unit BERT model for lips reading task for the Austrian Red Cross challenge. Integrated the model into the web app, which allowed the Red Cross team to communicate in a very noisy environment
    }
    \tech{
    FastAPI, Next.js
    }
}

\experience{G20 Simulation Participant}
{Planet Needs YOUth}{May 2023}{}
{
    \achievement{
    I won an opportunity to participates in the G20 Simulation organized by ISPI for 3 days and held a position of the presidency (India) during the event. 
    }
    \tech{
    Negotiation, Cross-cultural communication, Presenting
    }
}

\experience{Hackathon finalist}
{Loyalty Evolution der RBI}{Mar 2023}{}
{
    \achievement{
    Created a smart contract and an accompanying app, which utilized dynamic NFTs as a wallet and metadata as the maskot (Sumsi) characteristics. The usecase was to attract more customers and introduce coupons and cashback to the existing online banking at RBI.
    }
    \tech{
    Next.js, Solidity
    }
}

\experience{3rd place Winner}
{Gastro Hackathon}{Nov 2022}{}
{
    \achievement{
    Our team created a Chrome extention that translated and summarized the AMS website to allow foreign talent easier access to job postings.
    }
    \tech{
    Java
    }
}

\experience{1st place Winner}
{Tourism Data Challenge}{Sep 2022}{}
    {
    \achievement{
    Won a hackathon organized by the Österreich Werbung with the project NFHotel, which further transformed to susteam. The proposed solution to attracting tourists to Austrian destinations was to issue collectable NFT stamps as a reward for choosing sustainable destinations. 
    }
    \tech{
    Next.js, Solidity
    }
}

\end{document}